### 2020-06-15 docs/LaTex/Paper.tex
Minor fixes

% Paper geometry
\usepackage[a4paper,left=3cm,right=2.5cm,vmargin=2.5cm]{geometry}
% \usepackage[showframe,a4paper,left=3cm,right=2.5cm,vmargin=2.5cm]{geometry}

@@

% To produce a spanish automated output, for instance, TOC is called 'Índice' and
% References is called 'Referencias'
\usepackage[english]{babel}

@@

Then it would be necessary to install the GPIO access library from Raspberry repositories, \cmd{sudo apt install wiringpi}. After this, the reader will be in position to clone the controller from the github repo \cite{Dragino_DualChannelController_Rpi}

@@

Once the controller is compiled, the reader must check the contents of \cmd{global\_conf.json}, for this projects, due it is using the LoRa GPS HAT Single Channel LoRa \cite{DraginoRpiHat}, the pins configuration in \cmd{global\_conf.json} must be

@@

I order to obtain the gateway ID the reader will need to perform the following command to run for the first time the \cmd{dual\_chan\_pkt\_fwd} binary, i.e. once the compilation process has produced the \cmd{dual\_chan\_pkt\_fwd} is necessary to run it directly to check the terminal output and find for the gateway ID.

>>>>

% Document geometry
\usepackage[a4paper,left=3cm,right=2.5cm,vmargin=2.5cm]{geometry}
% \usepackage[showframe,a4paper,left=3cm,right=2.5cm,vmargin=2.5cm]{geometry}

@@

% To produce a spanish automated output, for instance, TOC is called 'Índice' and
% References is called 'Referencias' (in this case I prefer english)
\usepackage[english]{babel}

@@

Then it would be necessary to install the GPIO access library from Raspberry repositories, \cmd{sudo apt install wiringpi}. After this, the reader will be in position to clone the controller from the github repository \cite{Dragino_DualChannelController_Rpi}

@@

Once the controller is compiled, the reader must check the contents of \cmd{global\_conf.json}, for this projects, due it is using the LoRa GPS HAT Single Channel LoRa \cite{DraginoRpiHat}, the pins configuration in \cmd{global\_conf.json} must be the following as stated by \cite{Dragino_DualChannelController_Rpi}

@@

I order to obtain the gateway ID the reader will need to perform the following command to run for the first time the \cmd{dual\_chan\_pkt\_fwd} binary, i.e. once the compilation process has produced the \cmd{dual\_chan\_pkt\_fwd} binary is necessary to run it directly to check the terminal output and find for the gateway ID.
